Response to the defense feedback

### 2021-06-19 Chapter-2/Chapter-2.tex
Updates from Overleaf

Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between a cache miss and cache hit. The core-private caches (e.g., L1 and L2) are traditionally set-associate cache. The cache is divided into different cache sets, and each cache set is made up of several cache lines. Typically, the smallest storage unit in a CPU cache is a cache line. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. We introduce two common attack strategies, namely Prime+Probe and Flush+Reload.

\textbf{Prime+Probe.} Prime+Probe targets a single cache set.
An attacker primes the cache set with its own data and waits until the victim executes the program. Then the attacker probes the cache by reading previously loaded data. If the victim accesses the cache set and evicts some lines of the data, the attacker will experience a slow measurement. Under the circumstance, the attacker can know that the victim must have touched some data that map to the same cache set.

>>>>

Cache channels~\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last,184415} rely on the time difference between a cache miss and cache hit. The core-private caches (e.g., L1 and L2) are traditionally set-associate cache. The cache is divided into different cache sets, and each cache set is made up of several cache lines. Typically, the smallest storage unit in a CPU cache is a cache line. Cache channel attacks can observe cache accesses at the level of cache sets, cache lines or other granularities. We introduce two common attack strategies, namely Prime+Probe~\cite{liu2015last}  and Flush+Reload~\cite{yarom2014flush+}.

\textbf{Prime+Probe.} Prime+Probe targets a single cache set.
An attacker primes the cache set with its own data and waits until the victim executes the program. Then the attacker probes the cache by reading previously loaded data. If the victim accesses the cache set and evicts the data loaded by the attacker, the attacker will experience a slow measurement. Under the circumstance, the attacker can know that the victim must have touched some data that maps to the same cache set.
